
---
output:
  html_document:
    css: style.css
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(cowplot)
library(ggplot2)
library(magick)
library(ggpubr)

```

# **Effective moves after migration**

The following figures illustrate the effective moves after migration.

## **50D scenario**


<details>
<summary><b>Function:</b> <i>f1</i></summary>
<p>

```{r f1}
s3 <- ggdraw() + draw_image("effective_moves_images50/f1_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f1_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f1_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f1_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f1_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f2</i></summary>
<p>

```{r f2}
s3 <- ggdraw() + draw_image("effective_moves_images50/f2_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f2_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f2_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f2_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f2_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f3</i></summary>
<p>

```There were no migrations in this function.```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f4</i></summary>
<p>

```{r f4}
s3 <- ggdraw() + draw_image("effective_moves_images50/f4_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f4_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f4_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f4_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f4_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f5</i></summary>
<p>

```{r f5}
s3 <- ggdraw() + draw_image("effective_moves_images50/f5_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f5_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f5_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f5_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f5_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f6</i></summary>
<p>

```{r f6}
s3 <- ggdraw() + draw_image("effective_moves_images50/f6_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f6_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f6_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f6_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f6_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f7</i></summary>
<p>

```{r f7}
s3 <- ggdraw() + draw_image("effective_moves_images50/f7_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f7_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f7_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f7_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f7_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f8</i></summary>
<p>

```{r f8}
s3 <- ggdraw() + draw_image("effective_moves_images50/f8_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f8_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f8_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f8_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f8_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>

<details>
<summary><b>Function:</b> <i>f9</i></summary>
<p>

```{r f9}
s3 <- ggdraw() + draw_image("effective_moves_images50/f9_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f9_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f9_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f9_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f9_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f10</i></summary>
<p>

```{r f10}
s3 <- ggdraw() + draw_image("effective_moves_images50/f10_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f10_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f10_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f10_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f10_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>





<details>
<summary><b>Function:</b> <i>f11</i></summary>
<p>

```{r f11}
s3 <- ggdraw() + draw_image("effective_moves_images50/f11_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f11_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f11_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f11_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f11_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f12</i></summary>
<p>

```{r f12}
s3 <- ggdraw() + draw_image("effective_moves_images50/f12_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f12_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f12_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f12_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f12_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f13</i></summary>
<p>

```{r f13}
s3 <- ggdraw() + draw_image("effective_moves_images50/f13_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f13_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f13_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f13_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f13_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f14</i></summary>
<p>

```{r f14}
s3 <- ggdraw() + draw_image("effective_moves_images50/f14_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f14_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f14_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f14_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f14_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f15</i></summary>
<p>

```{r f15}
s3 <- ggdraw() + draw_image("effective_moves_images50/f15_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f15_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f15_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f15_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f15_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f16</i></summary>
<p>

```{r f16}
s3 <- ggdraw() + draw_image("effective_moves_images50/f16_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f16_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f16_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f16_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f16_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f17</i></summary>
<p>

```{r f17}
s3 <- ggdraw() + draw_image("effective_moves_images50/f17_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f17_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f17_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f17_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f17_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f18</i></summary>
<p>

```{r f18}
s3 <- ggdraw() + draw_image("effective_moves_images50/f18_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f18_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f18_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f18_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f18_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f19</i></summary>
<p>

```{r f19}
s3 <- ggdraw() + draw_image("effective_moves_images50/f19_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f19_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f19_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f19_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f19_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f20</i></summary>
<p>

```{r f20}
s3 <- ggdraw() + draw_image("effective_moves_images50/f20_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f20_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f20_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f20_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f20_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f21</i></summary>
<p>

```{r f21}
s3 <- ggdraw() + draw_image("effective_moves_images50/f21_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f21_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f21_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f21_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f21_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f22</i></summary>
<p>

```{r f22}
s3 <- ggdraw() + draw_image("effective_moves_images50/f22_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f22_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f22_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f22_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f22_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f23</i></summary>
<p>

```{r f23}
s3 <- ggdraw() + draw_image("effective_moves_images50/f23_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f23_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f23_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f23_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f23_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f24</i></summary>
<p>

```{r f24}
s3 <- ggdraw() + draw_image("effective_moves_images50/f24_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f24_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f24_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f24_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f24_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f25</i></summary>
<p>

```{r f25}
s3 <- ggdraw() + draw_image("effective_moves_images50/f25_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f25_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f25_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f25_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f25_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f26</i></summary>
<p>

```{r f26}
s3 <- ggdraw() + draw_image("effective_moves_images50/f26_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f26_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f26_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f26_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f26_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f27</i></summary>
<p>

```{r f27}
s3 <- ggdraw() + draw_image("effective_moves_images50/f27_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f27_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f27_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f27_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f27_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f28</i></summary>
<p>

```{r f28}
s3 <- ggdraw() + draw_image("effective_moves_images50/f28_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f28_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f28_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f28_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f28_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f29</i></summary>
<p>

```{r f29}
s3 <- ggdraw() + draw_image("effective_moves_images50/f29_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f29_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f29_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f29_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f29_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f30</i></summary>
<p>

```{r f30}
s3 <- ggdraw() + draw_image("effective_moves_images50/f30_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images50/f30_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images50/f30_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images50/f30_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images50/f30_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




## **100D scenario**

<details>
<summary><b>Function:</b> <i>f1</i></summary>
<p>

```{r f1_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f1_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f1_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f1_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f1_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f1_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f2</i></summary>
<p>

```{r f2_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f2_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f2_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f2_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f2_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f2_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>

<details>
<summary><b>Function:</b> <i>f3</i></summary>
<p>

```There were no migrations in this function.```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f4</i></summary>
<p>

```{r f4_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f4_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f4_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f4_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f4_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f4_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f5</i></summary>
<p>

```{r f5_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f5_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f5_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f5_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f5_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f5_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f6</i></summary>
<p>

```{r f6_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f6_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f6_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f6_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f6_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f6_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f7</i></summary>
<p>

```{r f7_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f7_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f7_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f7_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f7_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f7_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f8</i></summary>
<p>

```{r f8_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f8_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f8_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f8_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f8_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f8_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>

<details>
<summary><b>Function:</b> <i>f9</i></summary>
<p>

```{r f9_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f9_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f9_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f9_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f9_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f9_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f10</i></summary>
<p>

```{r f10_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f10_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f10_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f10_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f10_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f10_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>





<details>
<summary><b>Function:</b> <i>f11</i></summary>
<p>

```{r f11_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f11_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f11_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f11_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f11_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f11_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f12</i></summary>
<p>

```{r f12_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f12_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f12_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f12_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f12_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f12_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f13</i></summary>
<p>

```{r f13_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f13_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f13_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f13_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f13_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f13_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f14</i></summary>
<p>

```{r f14_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f14_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f14_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f14_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f14_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f14_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f15</i></summary>
<p>

```{r f15_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f15_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f15_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f15_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f15_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f15_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f16</i></summary>
<p>

```{r f16_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f16_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f16_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f16_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f16_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f16_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f17</i></summary>
<p>

```{r f17_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f17_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f17_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f17_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f17_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f17_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f18</i></summary>
<p>

```{r f18_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f18_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f18_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f18_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f18_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f18_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f19</i></summary>
<p>

```{r f19_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f19_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f19_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f19_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f19_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f19_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f20</i></summary>
<p>

```{r f20_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f20_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f20_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f20_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f20_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f20_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f21</i></summary>
<p>

```{r f21_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f21_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f21_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f21_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f21_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f21_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f22</i></summary>
<p>

```{r f22_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f22_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f22_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f22_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f22_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f22_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f23</i></summary>
<p>

```{r f23_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f23_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f23_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f23_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f23_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f23_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f24</i></summary>
<p>

```{r f24_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f24_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f24_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f24_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f24_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f24_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f25</i></summary>
<p>

```{r f25_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f25_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f25_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f25_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f25_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f25_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f26</i></summary>
<p>

```{r f26_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f26_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f26_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f26_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f26_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f26_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f27</i></summary>
<p>

```{r f27_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f27_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f27_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f27_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f27_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f27_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f28</i></summary>
<p>

```{r f28_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f28_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f28_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f28_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f28_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f28_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f29</i></summary>
<p>

```{r f29_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f29_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f29_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f29_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f29_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f29_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f30</i></summary>
<p>

```{r f30_100}
s3 <- ggdraw() + draw_image("effective_moves_images100/f30_aepd_teda_cloud.png", scale = 1)
s2 <- ggdraw() + draw_image("effective_moves_images100/f30_aepd_teda_best.png", scale = 1)
s1 <- ggdraw() + draw_image("effective_moves_images100/f30_aepd_best.png", scale = 1)
fix <- ggdraw() + draw_image("effective_moves_images100/f30_fix.png", scale = 1)
prob <- ggdraw() + draw_image("effective_moves_images100/f30_prob.png", scale = 1)

ggarrange(s3,s2,s1,fix,prob,
          labels = c("S3", "S2", "S1", "FIX", "PROB"),
          hjust = c(-1, -1),
          font.label = list(size = 20),
          ncol = 3, nrow = 2)

```

</p>
</details>
