---
output:
  html_document:
    css: style.css
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(cowplot)
library(ggplot2)
library(magick)
library(ggpubr)

```

# **Average error**

Figures illustrate the Boxplots and Kruskal–Wallis test results for different strategies for average error values.

## **50D scenario**


<details>
<summary><b>Function:</b> <i>f1</i></summary>
<p>

```Standard error of all strategies equal to or very close to zero.```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f2</i></summary>
<p>

```Standard error of all strategies equal to or very close to zero.```

</p>
</details>

<details>
<summary><b>Function:</b> <i>f3</i></summary>
<p>

```Standard error of all strategies equal to or very close to zero.```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f4</i></summary>
<p>

```{r f4}
ggdraw() + draw_image("error_images_50/f4.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f5</i></summary>
<p>

```{r f5}
ggdraw() + draw_image("error_images_50/f5.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f6</i></summary>
<p>

```{r f6}
ggdraw() + draw_image("error_images_50/f6.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f7</i></summary>
<p>

```Standard error of all strategies equal to or very close to zero.```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f8</i></summary>
<p>

```{r f8}
ggdraw() + draw_image("error_images_50/f8.png", scale = 1)
```

</p>
</details>

<details>
<summary><b>Function:</b> <i>f9</i></summary>
<p>

```{r f9}
ggdraw() + draw_image("error_images_50/f9.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f10</i></summary>
<p>

```{r f10}
ggdraw() + draw_image("error_images_50/f10.png", scale = 1)
```

</p>
</details>





<details>
<summary><b>Function:</b> <i>f11</i></summary>
<p>

```{r f11}
ggdraw() + draw_image("error_images_50/f11.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f12</i></summary>
<p>

```{r f12}
ggdraw() + draw_image("error_images_50/f12.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f13</i></summary>
<p>

```{r f13}
ggdraw() + draw_image("error_images_50/f13.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f14</i></summary>
<p>

```{r f14}
ggdraw() + draw_image("error_images_50/f14.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f15</i></summary>
<p>

```{r f15}
ggdraw() + draw_image("error_images_50/f15.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f16</i></summary>
<p>

```{r f16}
ggdraw() + draw_image("error_images_50/f16.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f17</i></summary>
<p>

```{r f17}
ggdraw() + draw_image("error_images_50/f17.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f18</i></summary>
<p>

```{r f18}
ggdraw() + draw_image("error_images_50/f18.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f19</i></summary>
<p>

```{r f19}
ggdraw() + draw_image("error_images_50/f19.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f20</i></summary>
<p>

```{r f20}
ggdraw() + draw_image("error_images_50/f20.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f21</i></summary>
<p>

```{r f21}
ggdraw() + draw_image("error_images_50/f21.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f22</i></summary>
<p>

```{r f22}
ggdraw() + draw_image("error_images_50/f22.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f23</i></summary>
<p>

```Standard error of all strategies equal to or very close to zero.```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f24</i></summary>
<p>

```{r f24}
ggdraw() + draw_image("error_images_50/f24.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f25</i></summary>
<p>

```{r f25}
ggdraw() + draw_image("error_images_50/f25.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f26</i></summary>
<p>

```{r f26}
ggdraw() + draw_image("error_images_50/f26.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f27</i></summary>
<p>

```{r f27}
ggdraw() + draw_image("error_images_50/f27.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f28</i></summary>
<p>

```{r f28}
ggdraw() + draw_image("error_images_50/f28.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f29</i></summary>
<p>

```{r f29}
ggdraw() + draw_image("error_images_50/f29.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f30</i></summary>
<p>

```{r f30}
ggdraw() + draw_image("error_images_50/f30.png", scale = 1)
```

</p>
</details>




## **100D scenario**

<details>
<summary><b>Function:</b> <i>f1</i></summary>
<p>

```{r f1_100}
ggdraw() + draw_image("error_images_100/f1.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f2</i></summary>
<p>

```Standard error of all strategies equal to or very close to zero.```

</p>
</details>

<details>
<summary><b>Function:</b> <i>f3</i></summary>
<p>

```Standard error of all strategies equal to or very close to zero.```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f4</i></summary>
<p>

```{r f4_100}
ggdraw() + draw_image("error_images_100/f4.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f5</i></summary>
<p>

```{r f5_100}
ggdraw() + draw_image("error_images_100/f5.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f6</i></summary>
<p>

```{r f6_100}
ggdraw() + draw_image("error_images_100/f6.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f7</i></summary>
<p>

```{r f7_100}
ggdraw() + draw_image("error_images_100/f7.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f8</i></summary>
<p>

```{r f8_100}
ggdraw() + draw_image("error_images_100/f8.png", scale = 1)
```

</p>
</details>

<details>
<summary><b>Function:</b> <i>f9</i></summary>
<p>

```{r f9_100}
ggdraw() + draw_image("error_images_100/f9.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f10</i></summary>
<p>

```{r f10_100}
ggdraw() + draw_image("error_images_100/f10.png", scale = 1)
```

</p>
</details>





<details>
<summary><b>Function:</b> <i>f11</i></summary>
<p>

```{r f11_100}
ggdraw() + draw_image("error_images_100/f11.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f12</i></summary>
<p>

```{r f12_100}
ggdraw() + draw_image("error_images_100/f12.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f13</i></summary>
<p>

```{r f13_100}
ggdraw() + draw_image("error_images_100/f13.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f14</i></summary>
<p>

```{r f14_100}
ggdraw() + draw_image("error_images_100/f14.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f15</i></summary>
<p>

```{r f15_100}
ggdraw() + draw_image("error_images_100/f15.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f16</i></summary>
<p>

```{r f16_100}
ggdraw() + draw_image("error_images_100/f16.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f17</i></summary>
<p>

```{r f17_100}
ggdraw() + draw_image("error_images_100/f17.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f18</i></summary>
<p>

```{r f18_100}
ggdraw() + draw_image("error_images_100/f18.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f19</i></summary>
<p>

```{r f19_100}
ggdraw() + draw_image("error_images_100/f19.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f20</i></summary>
<p>

```{r f20_100}
ggdraw() + draw_image("error_images_100/f20.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f21</i></summary>
<p>

```{r f21_100}
ggdraw() + draw_image("error_images_100/f21.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f22</i></summary>
<p>

```{r f22_100}
ggdraw() + draw_image("error_images_100/f22.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f23</i></summary>
<p>

```{r f23_100}
ggdraw() + draw_image("error_images_100/f23.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f24</i></summary>
<p>

```{r f24_100}
ggdraw() + draw_image("error_images_100/f24.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f25</i></summary>
<p>

```{r f25_100}
ggdraw() + draw_image("error_images_100/f25.png", scale = 1)
```

</p>
</details>




<details>
<summary><b>Function:</b> <i>f26</i></summary>
<p>

```{r f26_100}
ggdraw() + draw_image("error_images_100/f26.png", scale = 1)
```

</p>
</details>


<details>
<summary><b>Function:</b> <i>f27</i></summary>
<p>

```{r f27_100}
ggdraw() + draw_image("error_images_100/f27.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f28</i></summary>
<p>

```{r f28_100}
ggdraw() + draw_image("error_images_100/f28.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f29</i></summary>
<p>

```{r f29_100}
ggdraw() + draw_image("error_images_100/f29.png", scale = 1)
```

</p>
</details>



<details>
<summary><b>Function:</b> <i>f30</i></summary>
<p>

```{r f30_100}
ggdraw() + draw_image("error_images_100/f30.png", scale = 1)
```

</p>
</details>